12th International Satisfiability Modulo Theories Competition (SMT-COMP 2017): Rules and Procedures

### 2017-04-21 rules/rules17.tex
Minor.

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Matthias Heizmann, Albert Oliveras, Aaron Stump, and Tjark Weber.}
describes the rules and competition procedures for SMT-COMP~2017.  The
principal changes from the previous competition rules are the
following:
\begin{itemize}
\item Submission of accompanying information for solvers is via a web
  form (rather than by email to the organizers).  \emph{Rationale:}
  Email submissions were often incomplete, leading to ambiguity and
  further inquiries.  The form provides a more structured way of
  submitting information.
\item Benchmarks with unknown status will be eligible for the
  competition's main track.  In 2016, solver performance on benchmarks
  with unknown status was evaluated but reported separately; in 2017,
  it will directly affect the competition results.  \emph{Rationale:}
  Using only benchmarks with known status (i.e., benchmarks that have
  been solved before) to determine the competition results unjustly
  favors imitation of existing solvers over true innovation.
\item Benchmarks will likely use (a subset of) version~2.5 of the
  SMT-LIB language.  \emph{Rationale:} This is the latest version of
  the SMT-LIB language.  Its use had been announced for SMT-COMP 2016
  already, but was delayed because the SMT-LIB benchmark collection
  had not been updated.  Solvers should ideally support both
  versions~2.0 and~2.5; the latter is largely backwards-compatible.
\item Benchmarks that use partial bit-vector functions, such as
  \texttt{bvudiv}, may become eligible for the competition again,
  provided the semantics of these functions (according to SMT-LIB) is
  changed to agree with existing solver implementations, and the
  status of affected SMT-LIB benchmarks is updated accordingly.
  \emph{Rationale:} The semantics of these functions has been
  discussed for a long time, and it appears that a conclusion has
  finally been reached.
\item The penalty for erroneous results in the competition-wide
  scoring is changed from the number of errors to a fixed constant
  (multiplied by the weight of the respective division).
  \emph{Rationale:} The weight already takes the number of benchmarks
  in a division into account; multiplying it by the number of errors
  overemphasizes large divisions.
\item The unsat-core track, which was re-introduced in 2016, is no
  longer experimental.  Its divisions will be considered competitive
  if the necessary requirements (see Section~\ref{sec:scoring}) are
  met.  \emph{Rationale:} Rules and tool support for the unsat-core
  track proved sufficiently stable in 2016.
\item The competition may feature experimental divisions for
  benchmarks that use algebraic datatypes, provided suitable
  benchmarks are available.  \emph{Rationale:} Algebraic datatypes are
  specified in the draft SMT-LIB~2.6 standard, which is expected to
  become official in the near future, and are already supported by
  some solvers.
\end{itemize}

@@

\header{Benchmark selection.}
%
The competition will use a large subset of SMT-LIB benchmarks.  The
benchmark pool is culled as follows:
\begin{enumerate}
\item \emph{Remove inappropriate benchmarks.} The competition
  organizers may remove benchmarks that are deemed
  inappropriate\footnote{In 2017, this may (again) include all
    benchmarks that use partial or underspecified functions, e.g.,
    \texttt{bvudiv}, \texttt{fp.min}, unless their semantics can be
    resolved in time for the competition.}  or uninteresting for
  competition, or cut the size of certain benchmark families to avoid
  their over-representation.  SMT-COMP attempts to give preference to
  benchmarks that are ``real-world,'' in the sense of coming from or
  having some intended application outside SMT.
\item \emph{Remove incremental benchmarks whose first \akey{check-sat}
  command has unknown status.}  Incremental benchmarks may contain
  multiple \akey{check-sat} commands, each with its own status.  If an
  incremental benchmark contains a \akey{check-sat} command whose
  status is unknown, only the prefix of the benchmark up to the
  preceding \akey{check-sat} command is eligible for the application
  track of the competition; if the benchmark's first \akey{check-sat}
  command has unknown status, the entire benchmark is
  ineligible.\footnote{It might be desirable to also include
    \akey{check-sat} commands with unknown status in the application
    track (for the same reasons they are now included in the main
    track), but this would require substantial changes to the trace
    executor and scoring tools.}
\end{enumerate}
%
All remaining benchmarks are used for the competition.  There will be
no further selection of benchmarks, e.g., based on benchmark
difficulty or benchmark category.

>>>>

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Matthias Heizmann, Albert Oliveras, Aaron Stump, and Tjark Weber.}
describes the rules and competition procedures for SMT-COMP~2017.  The
principal changes from the previous competition rules are the
following:
\begin{itemize}
\item Submission of accompanying information for solvers is via a web
  form (rather than by email to the organizers).  \emph{Rationale:}
  Email submissions were often incomplete, leading to ambiguity and
  further inquiries.  The form provides a more structured way of
  submitting information.
\item Benchmarks may use (a subset of) version~2.5 of the SMT-LIB
  language.  \emph{Rationale:} This is the latest version of the
  SMT-LIB language.  Its use had been announced for SMT-COMP 2016
  already, but was delayed because the SMT-LIB benchmark collection
  had not been updated.  Solvers should ideally support both
  versions~2.0 and~2.5; the latter is largely backwards-compatible.
\item Benchmarks that use partial bit-vector functions, such as
  \texttt{bvudiv}, or underspecified floating-point functions, such as
  \texttt{fp.min}, may become eligible for the competition again,
  provided (i)~the semantics of these functions agrees with existing
  solver implementations, and (ii)~the status of affected benchmarks
  in SMT-LIB is not incorrect.  \emph{Rationale:} The semantics of
  these functions had been under discussion, and it appears that a
  conclusion has finally been reached.
\item Benchmarks with unknown status will be eligible for the
  competition's main track.  In 2016, solver performance on benchmarks
  with unknown status was evaluated but reported separately; in 2017,
  it will directly affect the competition results.  \emph{Rationale:}
  Using only benchmarks with known status (i.e., benchmarks that have
  been solved before) to determine the competition results unjustly
  favors imitation of existing solvers over true innovation.
\item In the competition-wide scoring, the (per-division) penalty for
  erroneous results is changed from the number of errors to a fixed
  constant (multiplied by the weight of the respective division).
  \emph{Rationale:} The weight already takes the number of benchmarks
  in the division into account; multiplying it by the number of errors
  overemphasizes large divisions.
\item The unsat-core track, which was re-introduced in 2016, is no
  longer experimental.  Its divisions will be considered competitive
  if the necessary requirements (see Section~\ref{sec:scoring}) are
  met.  \emph{Rationale:} Rules and tool support for the unsat-core
  track proved sufficiently stable in 2016.
\item The competition may feature experimental divisions for
  benchmarks that use algebraic datatypes, provided suitable
  benchmarks are available.  \emph{Rationale:} Algebraic datatypes are
  specified in the draft SMT-LIB~2.6 standard, which is expected to
  become official in the near future, and are already supported by
  some solvers.
\end{itemize}

@@

\header{Benchmark selection.}
%
The competition will use a large subset of SMT-LIB benchmarks.  The
benchmark pool is culled as follows:
\begin{enumerate}
\item \emph{Remove inappropriate benchmarks.} The competition
  organizers may remove benchmarks that are deemed
  inappropriate\footnote{In previous years, this included all
    benchmarks that use partial or underspecified functions, e.g.,
    \texttt{bvudiv}, \texttt{fp.min}.  Whether these benchmarks are
    included in 2017 is yet to be decided.} or uninteresting for
  competition, or cut the size of certain benchmark families to avoid
  their over-representation.  SMT-COMP attempts to give preference to
  benchmarks that are ``real-world,'' in the sense of coming from or
  having some intended application outside SMT.
\item \emph{Remove incremental benchmarks whose first \akey{check-sat}
  command has unknown status.}  Incremental benchmarks may contain
  multiple \akey{check-sat} commands, each with its own status.  If an
  incremental benchmark contains a \akey{check-sat} command whose
  status is unknown, only the prefix of the benchmark up to the
  preceding \akey{check-sat} command is eligible for the application
  track of the competition; if the benchmark's first \akey{check-sat}
  command has unknown status, the entire benchmark is
  ineligible.\footnote{It might be desirable to also include
    \akey{check-sat} commands with unknown status in the application
    track (for the same reasons they are now included in the main
    track), but this would require substantial changes to the trace
    executor and scoring tools.}
\end{enumerate}
%
All remaining benchmarks are used for the competition.  There will be
no further selection of benchmarks, e.g., based on benchmark
difficulty or benchmark category.
